---
title: "Week 11: Lab - Build Your Own Shiny App"
author: '[Victor Arencibia]'
date: '[4/3/2022]'
output: html_document
---

---

# Instructions
Create a scatter plot interactive application. In this application, use the 
census data from earlier in the book, and let the user determine the X-axis, 
the Y-axis, the color (optional), and the size based on what the user would 
like to see. To do this, you will need multiple-choice menus, one for each 
selection the user needs to make. You can do this by following the direction 
written in the text book. Enjoy. 

**For your information:**   
The data is available through this link: 

* http://www2.census.gov/programs-surveys/popest/tables/2010-2011/state/totals/nst-est2011-01.csv


Add all of your libraries that you use for this assignment here.
```{r setup}
# Add your library below.

library(shiny)
library(ggplot2)
library(ggmap)
```

---

# Step 1 - Build the UI
Build the UI below.

```{r, "Step 1"}
ui <- fluidPage(
    selectInput("x", "x:",
                c("july population" = "july11pop",
                  "region of country" = "region",
                  "change in population" = "popChange",
                  "Percent change in population" = "percentChange")),
    selectInput("y", "y:",
                c("july population" = "july11pop",
                  "region of country" = "region",
                  "change in population" = "popChange",
                  "Percent change in population" = "percentChange")),
    selectInput("s", "size:",
                c("july population" = "july11pop",
                  "region of country" = "region",
                  "change in population" = "popChange",
                  "Percent change in population" = "percentChange")),
    plotOutput("scatterplot")
)

```

---

# Step 2 - Build the Server
Build the Server below.
```{r, "Step 2"}
server <- function(input, output) {
    
    dfStates <- readCensus()
    dfStates <- dfStates[dfStates$stateName != 
                             "District of Columbia", ]
    
    dfStates$region <- state.region
    dfStates$stateName <- tolower(dfStates$stateName)
    dfStates$popChange <- dfStates$july11pop - dfStates$july10pop
    dfStates$percentChange <- dfStates$popChange/dfStates$july10pop * 100
    
    us <- map_data("state")
    
    output$scatterplot <- renderPlot(
        ggplot(data = dfStates, aes_string(x = input$x, y = input$y, color=input$s)) + geom_point()
            
    )
}


```

---

# Step 3 - Create the Shiny App
Deploy the shiny app.
```{r, "Step 3"}

Numberize <- function(inputVector)
{
  #get rid of commas
  inputVector<-gsub(",","", inputVector)
  #get rid of spaces
  inputVector<-gsub(" ","", inputVector)
  
  return(as.numeric(inputVector))
}

readCensus <- function(){
  urlToRead<- 
  "http://www2.census.gov/programs-surveys/popest/tables/2010-2011/state/totals/nst-est2011-01.csv"
  testFrame <- read.csv(url(urlToRead))
  testFrame <-testFrame[-1:-8,]
  testFrame<-testFrame[,1:5]
  testFrame$stateName <- testFrame[,1]
  testFrame<-testFrame[,-1]
  testFrame<-testFrame[-52:-58,]

  testFrame$stateName <- gsub("\\.","",testFrame$stateName)

  testFrame$april10census <-Numberize(testFrame$X)
  testFrame$april10base <-Numberize(testFrame$X.1)
  testFrame$july10pop <-Numberize(testFrame$X.2)
  testFrame$july11pop <-Numberize(testFrame$X.3)
  testFrame <- testFrame[,-1:-4]
  rownames(testFrame) <- NULL
  
  return(testFrame)
}

shinyApp(ui = ui, server = server)

```
