---
title: "Week 11: Lab - Build Your Own Shiny App"
author: '[Name]'
date: '[Date]'
output: html_document
---

---

# Instructions
Create a scatter plot interactive application. In this application, use the 
census data from earlier in the book, and let the user determine the X-axis, 
the Y-axis, the color (optional), and the size based on what the user would 
like to see. To do this, you will need multiple-choice menus, one for each 
selection the user needs to make. You can do this by following the direction 
written in the text book. Enjoy. 

**For your information:**   
The data is available through this link: 

* http://www2.census.gov/programs-surveys/popest/tables/2010-2011/state/totals/nst-est2011-01.csv


Add all of your libraries that you use for this assignment here.
```{r setup}
# Add your library below.

library(shiny)
library(ggplot2)
```

---

# Step 1 - Build the UI
Build the UI below.

```{r, "Step 1"}
ui <- fluidPage(
  
  # Write your code here.
  
  )
```

---

# Step 2 - Build the Server
Build the Server below.
```{r, "Step 2"}
server <- function(input, output) {
  
 # Write your code here.
  
}

```

---

# Step 3 - Create the Shiny App
Deploy the shiny app.
```{r, "Step 3"}

# Write your code here.

```
