---
title: 'Week 9: Lab - Using aRules on the Titanic dataset '
author: '[Victor Arencibia]'
date: '[3/13/2022]'
output: html_document
---

---

# Instructions
Use the Titanic dataset to explore descriptive statistics, functions, and
association rules. Download the titanic dataset `titanic.raw.rdata` from one
of two locations:

- https://github.com/ethen8181/machine-learning/tree/master/association_rule/R
- https://sites.google.com/a/rdatamining.com/www/data/titanic.raw.rdata?attredirects=1
 
Note that it is not a cvs file, but rather an RData workspace. So, to load the 
data (assuming you saved it to the project's data folder), one would do:

``load("data/titanic.raw.rdata")``

You need to look at titanic.raw (the name of the R dataset)

``t <- titanic.raw``

Now that you have the datafile, do some descriptive statistics, getting some 
extra practice using R. Take the Quiz for Step 1 and 2. However your submission 
**MUST** include the process of you calculating the following values in Step 1 and 2.

---

```{r setup, message = FALSE}
# Add your library below.

#install.packages("dplyr")
library(dplyr)
#("arules")
library(arules)
#install.packages("arulesViz")
library(arulesViz)
require(datasets)
require(ggvis)
require(dplyr)
require(magrittr)
```

# Step 0 - Load the data
Using the instructions above, load the dataset and save it as `t`.

```{r, "Step 0"}
# Write your code below.

load("data/titanic.raw.rdata")
t <- titanic.raw

summary(t)
length(t)
str(t)
```
---


# Step 1 - Descriptive stats (0.5 point for each answer)

1. Compute the percentage of people that survived.
2. Compute the percentage of people that were children.
3. Compute the percentage of people that were female.
4. Finally, compute the percentage of people that were in first class.


# Write your code below.
```{r, "Step 1"}
totalpassengers <- tally(t)
totalpassengers

survivors <- filter(t, Survived == "Yes") 
totalsurvivors <- tally(survivors)
totalsurvivors
SurvivorPercent <- round((totalsurvivors/totalpassengers)*100)
SurvivorPercent
# 32%

Children <- filter(t, Age == "Child")
Children <- tally(Children)
ChildrenPercent <- round((Children/totalpassengers)*100)
ChildrenPercent
# 5%

  
Female <- filter(t, Sex == "Female") 
Female <- tally(Female)
FemalePercent <- round((Female/totalpassengers)*100)
FemalePercent
# 21 %


firstClass <- filter(t, Class == "1st")
firstClass <- tally(firstClass)
FirstClassPercent <- round((firstClass/totalpassengers)*100)
FirstClassPercent
# 15% 
```

---

# Step 2 - More descriptive stats (0.5 point for each answer)


1. What percentage of children survived? Your answer should be written such as # 13.75% of children survived
2. What percentage of female survived?
3. What percentage of first-class people survived?
4. What percentage of third-class people survived?

```{r, "Step 2"}
# Write your code below.

Children2 <- t %>%
  group_by(Age,Survived) %>%
  summarise (number = n()) %>%
  mutate (freq = (number / sum(number)*100))
View(Children2)
#52.29% of children survived.

Female2 <- t %>%
  group_by(Sex,Survived) %>%
  summarise (number = n()) %>%
  mutate (freq = (number / sum(number)*100))
View(Female2)
# 73.19 of females survived  

Class <- t %>%
  group_by(Class,Survived) %>%
  summarise (number = n()) %>%
  mutate (freq = (number / sum(number)*100))
Class
# 62.46 of first class survived
# 25.21 of Third class people survived

```

---

# Step 3 - Writing a function (0.5 point for each answer)

## Step 3.1 - Function 1
Write a function that returns a new dataframe of people that satisfies the 
specified criteria of sex, age, class and survived as parameters. I'm giving you 
the answer for this question:

```
myfunction1 <- function(a,b,c,d){
df1 <- t[t$Class == a,] # filter the data that satisfied the criteria that "Class" = a
df2 <- df1[df1$Sex == b,] # filter the data that satisfied the criteria that "Sex" = b
df3 <- df2[df2$Age == c,] # filter the data that satisfied the criteria that "Age" = c
df4 <- df3[df3$Survived == d,] # filter the data that satisfied the criteria that "Survived" = d
return(df4)}
# test the function with a sample data
myfunction1("1st","Female","Adult","No")
```

```{r, "Step 3.1"}
# Write your code below.

myfunction1 <- function(a,b,c,d){
df1 <- t[t$Class == a,] 
df2 <- df1[df1$Sex == b,] 
df3 <- df2[df2$Age == c,] 
df4 <- df3[df3$Survived == d,]
return(df4)}
# test the function with a sample data
myfunction1("1st","Female","Adult","No")

```

## Step 3.2 - Function 2
Write a function, using the previous function, that calculates the percentage 
(who lives, who dies) for a specified (parameters) of class, gender and age 
considering the entire number of data. The function passes four arguments. 
Include the following code properly in your function by improvising names of objects.

```
p <- nrow(df)/nrow(t) # calculate the percentage
```

```{r, "Step 3.2"}
# Write your code below.
df <- function(a,b,c,d){
df1 <- t[t$Class == a,] 
df2 <- df1[df1$Sex == b,] 
df3 <- df2[df2$Age == c,] 
df4 <- df3[df3$Survived == d,]
count(df4)
p <- (nrow(df4)/nrow(t))*100
return(p)}
# test the function with a sample data
df("1st","Female","Adult","No")



```

## Step 3.3 - Use the function (male)
Use the function to compare age and third-class male survival rates. 

```{r, "Step 3.3"}
# Write your code below.
df("3rd","Male","Child","Yes")

df("3rd","Male","Adult","Yes")
# 3.4% survival rate for Adult males in 3rd class



```
People in which category are more likely to survive? 

> [3rd class male adults]


## Step 3.4 - Use the function (female)
Use the function to compare age and first-class female survival rates.

```{r, "Step 3.4"}
# Write your code below.

df("1st", "Female","Child", "Yes")
df("1st", "Female","Adult", "Yes")

```
People in which category are more likely to survive? 

> [1st class female adults]

---

# Step 4 - Use aRules (0.5 point for each answer)

1. Use aRules to calculate some rules (clusters) for the titanic dataset.
2. Visualize the results.
3. Pick the three most interesting and useful rules. Explain these rules using natural language. **Answer this in the space provided below.**
4. How does this compare to the descriptive analysis we did on the same data set? 
Think critically. What was possible using one method that was not possible using 
the other method? **Answer this in the space provided below.**

```{r, "Step 4.1"}
# Write your code below.
t2 <- apriori(t, parameter = list(support=0.005,confidence=0.5))
plot(t2)
inspect(sort(t2,by="lift"))
inspect(sort(t2, by="support"))
inspect(sort(t2, by="confidence"))
```

**Answer part 3 and 4 below.**

> [The rules lift implies that 2nd class adults that survived were likely to be Female with a lift of 3.98 likelyhood. ]


