---
title: "Week 5: Lab - Word Cloud Chapter Challenge"
author: "Victor Arencibia"
date: "2/12/2022"
output: html_document
---

---

# Instructions
Create a word cloud using the `text` column from a real twitter dataset 
(sample.csv).

---

```{r setup, message = FALSE}
# Add your library below.

require(tm)
require(wordcloud)





```

# Step 1. Load and Clean the Data
Load in the `sample.csv` dataset from this project's data folder. 
Please make sure you transform the document to lowercase, delete stopwords & numbers & punctuation (1 point).

```{r, "Step 1"}
# Write your code below.

#install.packages("readxl")
library(readxl)
sampledf <- read.csv("data/sample.csv", stringsAsFactors = F)

head(sample)

tail(sampledf,20)
str(sampledf)


words.vec <- VectorSource(sampledf)
words.corpus <- Corpus(words.vec)

words.corpus <- tm_map(words.corpus, content_transformer(tolower))
words.corpus <- tm_map(words.corpus, removePunctuation)
words.corpus <- tm_map(words.corpus, removeNumbers)
words.corpus <- tm_map(words.corpus, removeWords, stopwords("english"))

tdm <- TermDocumentMatrix(words.corpus)

str(tdm)
inspect(tdm[1:15,1:15])


```

---

# Step 2. Adjust the Stopwords
Add "can" and "just" to the stopwords list (1 point). 

```{r, "Step 2"}
# Write your code below.
# I had to search google on how to add addition stopwords.

words.corpus <- tm_map(words.corpus, removeWords, c(stopwords("english"),"can", "just")) 


```

---

# Step 3. Adjust the Theme
Use five colors and "Accent" for color theme (1 point).

```{r, "Step 3"}
# Write your code below.

m <- as.matrix(tdm)
wordCounts <- rowSums(m)
wordCounts <- sort(wordCounts, decreasing = TRUE)
head(wordCounts)
cloudFrame<- data.frame(word=names(wordCounts), freq=wordCounts)
library(RColorBrewer)
wordcloud(names(wordCounts), wordCounts, min.freq=2, max.words=50, rot.per=0.35, 
          colors=brewer.pal(5, "Accent"))
                                             
?brewer.pal       

```

---

# Step 4. Analysis
Does the word cloud convey the key points of the document? (1 point). 


> I read through parts of the sample exel document and although I couldnt pinpoint exactly how many of each word there was there was definitely a theme. Considering its a post regarding 
Virgin America's reviews it doesnt surprise me that the most popular words were America, Virgin America, and time. The word cloud is an impressive visualization tool we as data scientist & engineers
could use once we are producing for a company. It allows the viewing to immediatly see what the most common words are, if Negative is in giant letters accross the screen than we know it's something
the orignization would have to address. Especially if we are using a file with thousands of variables and words. 

---

# Step 5. Compile
Submit the compiled file. 
The wordcloud may prevent you from compiling. If so, do the following: 

```
jpeg('p1.jpg')  
wordcloud(cloudFrame.t$word, cloudFrame.t$freq)  
dev.off()
```
This will make the graphs save in the current working directory. 

```{r, "Step 5"}
# Write your code below, if necessary.
#jpeg('p1.jpg')  
#wordcloud(names(wordCounts), wordCounts, min.freq=2, max.words=50, rot.per=0.35, 
          #colors=brewer.pal(5, "Accent"))  
#dev.off()

```