---
title: "Week 5: Lab - Word Cloud Chapter Challenge"
author: "[Name]"
date: "[Date]"
output: html_document
---

---

# Instructions
Create a word cloud using the `text` column from a real twitter dataset 
(sample.csv).

---

```{r setup, message = FALSE}
# Add your library below.



```

# Step 1. Load and Clean the Data
Load in the `sample.csv` dataset from this project's data folder. 
Please make sure you transform the document to lowercase, delete stopwords & numbers & punctuation (1 point).

```{r, "Step 1"}
# Write your code below.


```

---

# Step 2. Adjust the Stopwords
Add "can" and "just" to the stopwords list (1 point). 

```{r, "Step 2"}
# Write your code below.


```

---

# Step 3. Adjust the Theme
Use five colors and "Accent" for color theme (1 point).

```{r, "Step 3"}
# Write your code below.


```

---

# Step 4. Analysis
Does the word cloud convey the key points of the document? (1 point). 


> [Write your answer here]

---

# Step 5. Compile
Submit the compiled file. 
The wordcloud may prevent you from compiling. If so, do the following: 

```
jpeg('p1.jpg')  
wordcloud(cloudFrame.t$word, cloudFrame.t$freq)  
dev.off()
```
This will make the graphs save in the current working directory. 

```{r, "Step 5"}
# Write your code below, if necessary.


```